%!TEX root = ../template.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% acknowledgements.tex
%% NOVA thesis document file
%%
%% Text with acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\typeout{NT FILE acknowledgements.tex}%

\begin{ntacknowledgements}

First and foremost, I would like to express my sincere gratitude to my thesis supervisor, Carla Ferreira, for their invaluable guidance, insightful feedback, and unwavering support throughout this research endeavor. Their expertise and encouragement have been instrumental in shaping this work.

I am deeply thankful to Magda Encarnação, Team Leader from KLx, for their constructive criticism and valuable suggestions that significantly contributed to the refinement of this thesis.

I am grateful to the Department of Computer Science from NOVA University Lisbon, for providing the necessary resources and conducive research environment that facilitated the completion of this study.

Personal acknowledgements extend to my friends and family for their patience, understanding, and encouragement during this academic journey. Their unwavering belief in my abilities has been a constant source of motivation.

Lastly, I acknowledge that while there are conventions for acknowledgements, this section is a personal expression of gratitude. Each individual mentioned has played a pivotal role in shaping both my academic and personal growth, for which I am sincerely thankful.

\end{ntacknowledgements}