\typeout{NT FILE chapter5.tex}%

\chapter{Work Plan}
\label{cha:Work Plan}

\prependtographicspath{{Chapters/Figures/Covers/}}



The work plan for this thesis involves several key phases, each with specific tasks aimed at achieving the project's goals. The plan is structured to ensure a systematic approach to refactoring, version control implementation, deployment automation, and development of new features and integrations.

\section{Refactoring the Codebase}

\subsection{Analyze Current Structure}

Review existing profiles and permissions.
Identify areas with code duplication and other smells.
Document the current state for reference.


\subsection{Design New Matrix}

Develop a new matrix for profiles and permissions.
Ensure the new design reduces redundancy.
Validate the new matrix with stakeholders.


\subsection{Refactor Code}

Implement changes based on the new matrix.
Conduct peer reviews of refactored code.
Perform unit and integration testing.


\section{Correcting Anomalies in the Permission Catalog}

\subsection{Review Identified Anomalies}

Document the anomalies found.
Analyze the root causes.


\subsection{Implement Corrections}

Modify the code to correct anomalies.
Validate the corrections through testing.


\section{Implementing Version Control with GIT}

\subsection{Finalize Version Control Strategy}

Research and select the most suitable version control approach.
Document the chosen method.


\subsection{Educate Team}

Conduct training sessions on the new version control system.
Provide supporting materials and documentation.


\subsection{Implement Version Control}

Migrate code to the GIT repository.
Ensure all team members are using the new system correctly.


\section{Automating Deployment with GITLAB}

\subsection{Document Current Process}

Analyze and document the current deployment process.
Identify inefficiencies and shortcomings.


\subsection{Transition to Cloud-Based Deployment}

Evaluate the use of native development tools.
Implement the transition from a local to a cloud-based environment.


\subsection{Integrate with GITLAB}

Set up CI/CD pipelines in GITLAB.
Test automated deployment processes.


\section{Developing New Features and Integrations}

\subsection{Develop Integration for L684 SAS Serveur}

Analyze integration requirements.
Develop and test provisioning scripts.


\subsection{Develop Integration for L716-SIMPLISSIMO}

Gather integration requirements.
Create and validate manual provisioning scripts.


\subsection{Develop Integration for L099A-Tables START}

Identify necessary steps for integration.
Implement and test manual provisioning scripts.


\section{Gantt chart with tasks}


